---
title: "Reproducible Research: Peer Assessment 1"
author: "Cristina Velez"
date: "9/23/2020"
output: 
  html_document:
    keep_md: true
    highlight: pygments
    theme: spacelab
    toc: yes
header-includes: \usepackage{graphicx}
---

## Assignment Instructions

1. Code for reading in the dataset and/or processing the data.
2. Histogram of the total number of steps taken each day.
3. Mean and median number of steps taken each day.
4. Time series plot of the average number of steps taken
5. The 5-minute interval that, on average, contains the maximum number of steps.
6. Code to describe and show a strategy for imputing missing data.
7. Histogram of the total number of steps taken each day after missing values are imputed.
8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and    weekends.
9. All of the R code needed to reproduce the results (numbers, plots, etc.) in the report 

***
## Loading and preprocessing the data
**1. Code for reading the dataset and/or processing the data.**
```{r, libraries, message=FALSE}
# Libraries
library(ggplot2)
library(dplyr)
library(lubridate)
```
```{r, data}
#Loading and reading data
setwd("~/Documents/GitHub/RepData_PeerAssessment1/RepData_PeerAssessment1")
unzip("./activity.zip")
activityData <- read.csv("./activity.csv")
```
```{r, attributes, results='hide'}
#Exploring the datset
dim(activityData)
names(activityData)
head(activityData)
str(activityData)
```

```{r, dates}
#Transforming the date column into date format 
activityData$date<-ymd(activityData$date)
length(unique(activityData$date))
summary(activityData)
```







